%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Technical Engineer} % Job title
    {Artavision UG} % Organisation
    {Aachen, Germany} % Location
    {Mar 2026 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Launched and developed Cognimata, a platform for AI-powered workflow automation and agentic AI systems targeting business process optimization.}
        \item {Provide AI consultancy services, advising organizations on AI strategy, LLM integration, and the adoption of automation-first engineering practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (AI \& Machine Learning)} % Job title
    {INFORM GmbH} % Organisation
    {Aachen, Germany} % Location
    {Jun 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and deployed the department's MLOps platform, establishing end-to-end pipelines for model training, versioning, monitoring, and deployment.}
        \item {Developed AI-driven optimization software for container terminal logistics, improving scheduling and distribution efficiency across terminal operations.}
        \item {Contributed to the core Terminal Operating System (TOS), integrating machine learning modules to enhance real-time decision-making in port logistics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Research Intern} % Job title
    {Volkswagen AG} % Organisation
    {Wolfsburg, Germany} % Location
    {Jul 2024 - Mar 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and evaluated meta-learning strategies for automated deep learning model selection in automotive time-series forecasting as part of the R\&D team.}
        \item {Benchmarked transfer learning and few-shot learning approaches across multiple time-series datasets, demonstrating improved model adaptation under limited labeled data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Amadeus Leisure IT GmbH} % Organisation
    {Kohlscheid, Germany} % Location
    {Apr 2023 - Jun 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed RESTful microservices using OpenAPI specification to aggregate and deliver travel data across multiple destination endpoints.}
        \item {Automated CI/CD pipelines with Jenkins and deployed containerized services on Kubernetes, reducing manual deployment overhead and improving release reliability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Process Mining Intern} % Job title
    {Mercedes-Benz AG} % Organisation
    {Sindelfingen, Germany} % Location
    {Sep 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered an end-to-end data pipeline for detecting and monitoring Overall Equipment Effectiveness (OEE) across manufacturing production lines.}
        \item {Developed interactive visualization dashboards for real-time downtime analysis, enabling production managers to identify and address performance bottlenecks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data/Cloud Engineer} % Job title
    {Derak Cloud Ltd.} % Organisation
    {Shiraz, Iran} % Location
    {May 2021 - Oct 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained a multi-tenant SaaS platform providing CDN, IaaS, and Video-on-Demand services to enterprise customers.}
        \item {Architected data pipelines using message queues and brokers for real-time data replication and infrastructure monitoring.}
        \item {Built a real-time tweet processing and sentiment analysis application enabling data-driven advertising decisions by the marketing team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AI Intern} % Job title
    {Deed Asia Ltd.} % Organisation
    {Shiraz, Iran} % Location
    {Jul 2019 - Sep 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a License Plate Recognition (LPR) system combining OCR with YOLO-based object detection, trained on a custom-labeled dataset of Iranian license plates.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
